Magnetic Inhibition of Convection and the Fundamental Properties of Low--Mass Stars

### 2016-05-13 paper/ms.tex
addressed refs first comment

A 10 Myr magnetic isochrone naturally explains the factor of two age difference observed between high- and low-mass stars, provided the high-mass stars are not appreciably affected by additional non-standard physics (e.g., rotation). 
Figures~\ref{fig:ages}a and \ref{fig:ages}c (HR diagrams) {\bf show that a 10 Myr isochrone computed with equipartition magnetic fields} is shifted toward cooler temperatures and higher luminosities compared to a 10 Myr non-magnetic isochrone. Inhibition of convection by magnetic fields {\bf cools the stellar surface temperature thereby slowing} the contraction rate of young stars. Stars have a larger radius and a higher luminosity at a given age, as a result. The combination of cooler surface temperatures and higher luminosities {\bf makes} a 10 Myr magnetic isochrone look nearly identical to a 5 Myr non-magnetic isochrone for {\bf stars with} effective temperatures {\bf below about 5\,000~K. The magnetic stellar model isochrone lies on top of the 5 Myr standard model isochrone in Figs.~\ref{fig:ages}a and \ref{fig:ages}c and entirely within} the empirical stellar locus for low-mass stars in Upper Scorpius.

{\bf The magnetic model isochrone also correctly converges toward the 10 Myr standard model isochrone at warmer effective temperatures. To some degree, this  convergence reproduces an observed transition in the empirical HR diagram where the age inferred from standard model isochrones shifts from 5 Myr to 10 Myr. Below \teff~$\sim 5\,000$~K, the magnetic isochrone closely matches predictions from a 5 Myr standard model isochrone. Compare this to the small segment of the magnetic isochrone above \teff\ $\sim 6\,000$~K. Here, the magnetic isochrone traces the 10 Myr standard model isochrone. Although the model predicted transition appears to occur over approximately the correct effective temperature domain, Fig.~\ref{fig:ages}a shows a sharper transition from a magnetic to a non-magnetic sequence between $4\,500 <$ \teff/K $< 6\,000$ compared to model predictions. This is more clearly seen in Fig.~\ref{fig:empirical}, where the empirical median stellar locus exhibits a knee around \teff $\sim 4\,500$~K that roughly corresponds to the beginning of the transition region in Fig.~\ref{fig:ages}a. A distinct knee feature is absent from the magnetic model isochrone.}

%In magnetic model space, this temperature domain corresponds to masses between $1.40$ and $1.56$ \msun. Inspection of Fig.~\ref{fig:mrd} reveals this mass range corresponds precisely to where the rapid thinning of the convection zone occurs, as expected.}

\begin{figure}[t]
    \centering
    \includegraphics[width=0.90\linewidth]{USCO5_MR.eps}
    \caption{Mass-radius diagram for stars in eclipsing systems. {\bf Black points are from \citet{Kraus2015} and \citet{Alonso2015}, while gray points are taken from \citet{Lodieu2015} and \citet{David2016}.} Model predictions for magnetic and non-magnetic isochrones are the same as in Fig.~\ref{fig:ages}.}
    \label{fig:mrd}
\end{figure}

Moreover, inspection of the mass-radius diagram in Figure~\ref{fig:mrd} shows a 10 Myr magnetic isochrone provides reasonable agreement with the two low-mass eclipsing binary systems. It is apparent that magnetic inhibition of convection leads to more significant radius ``inflation'' at higher masses compared to at lower masses. This effect leads to a change in slope of the model predicted mass-radius relationship that is consistent with observations. Although agreement is good, it is not perfect. {\bf Depending on whether mass and radius estimates are adopted from \citet{Kraus2015} or \citet{David2016}, at 10 Myr the radii of the primary and secondary in UScoCTIO5 are either 3.2\% and 2.1\% (\citeauthor{Kraus2015}) larger than model predictions or 5.7\% and 6.6\% larger (\citeauthor{David2016}).} Similarly, models at 10 Myr predict radii that are 1.4\% too large and 1.5\% too small for the Ba and Bb components of HD 144548 at 10 Myr, respectively. An age between 9.0 and 9.5 Myr is preferred for UScoCTIO5, while 10 Myr is the best fit age for HD 144548 Ba/Bb.

This age spread could be indicative of an intrinsic age spread, but it is also possible {\bf to attribute this spread to errors in the mass and radius determinations of the eclipsing binary systems or to the fact} that the low-mass stars in UScoCTIO5 may require marginally stronger magnetic field strengths than are predicted from equipartition arguments. Nevertheless, it is encouraging that models provide this level of agreement with an age and surface magnetic field strengths determined \emph{a priori}.

\section{Discussion}
\label{sec:disc}
An age of {\bf 9 -- 10} Myr gives broad agreement across the HR and mass-radius diagrams. No stellar population in Upper Scorpius {\bf studied here robustly} supports the possibility that the median age of the association is 5 Myr. There are, however, still age discrepancies that must be addressed. As noted above, the median age for F-type stars appears to be a few million years older than stars of other spectral types. This {\bf discrepancy} is {\bf perplexing and deserves further investigation}, especially considering that potential missing physics in the models would likely conspire to make F-stars older, not younger. It should be noted that most F-type stars in Upper Scorpius are at a stage of evolution where models predict radii increase and subsequently decrease over a period of roughly 4 -- 8 Myr. {\bf The timescale for this process is} similar to the observed age discrepancy (see Fig.~\ref{fig:bump} in Sect.~\ref{sec:radius}) and may be indicative of potential shortcomings in existing model physics such as radiative opacities or nuclear reaction cross-sections.

{\bf Age discrepancies also exist with two B-type members of Upper Scorpius: \object{$\tau$ Sco} and \object{$\omega$ Sco}. They exhibit ages between 2 and 5 Myr depending on whether rotation is accounted for in stellar evolution models \citep{Pecaut2012}. Those authors show that there are four other B-type stars that have inferred ages consistent with the 10 Myr median age proposed here, if rotation is taken into account. Notably the four stars that appear older are known binary systems while the two seemingly younger stars do not have a detected companion \citep{Pecaut2012}. The presence of two seemingly young B-type stars may be leveraged to suggest there exists a young population of stars with ages around 5 Myr thus supporting the younger age for the low-mass stellar population and thereby doing away with the need for a magnetic field explanation. However, that scenario requires that the low-mass stars form almost exclusively in a later star formation episode than the higher mass population. Although we cannot definitively rule out this scenario, we find it unlikely and maintain that the {\bf median} age for the low-mass stars is too young compared to the rest of the stellar population in the absence of magnetic inhibition of convection.}

\subsection{Magnetic Field Evolution \& Radiative Core Growth}
\label{sec:dynamo}
% F --> G type members are bright (V < 10 mag) and could be accessible to ZDI. Perhaps we'd see changes in magnetic strengths or topologies stretching from late-G to late-F.

{\bf Figure~\ref{fig:ages} shows that a 10 Myr magnetic model isochrone agrees with predictions from a 5 Myr standard model isochrone for effective temperatures below about 5\,000~K, but traces a 10 Myr standard model isochrone above 6\,000~K. This suggests that magnetic inhibition of convection plays an important role in dictating the structure of cool low-mass stars, but the structure of warmer high-mass stars is relatively insensitive to the influence of magnetic fields. In between these two regimes, models predict a transition in which stars appear to exhibit a decreasing sensitivity to magnetic inhibition of convection as effective temperature increases. }

{\bf As was noted in Sect.~\ref{sec:results}, Figs.~\ref{fig:empirical} and \ref{fig:ages}a indicate that a similar transition occurs over roughly the same effective temperature domain in the empirical HR diagram of Upper Scorpius. Early- to mid-G stars in Upper Scorpius (\teff$ \sim 6\,000$~K) are best described by a 10 Myr standard stellar model isochrone. Instead of continuing to follow a 10 Myr standard model isochrone, late-G stars appear to be better represented by an isochrone intermediate between 5 and 10 Myr. This causes the empirical sequence to exhibit a shallower slope than standard model predictions between $5\,750 > T_{\rm eff} / {\rm K} > 4\,500$. 
That the shallower slope in the empirical HR diagram and the transition predicted by magnetic stellar models are coincident, suggests that the two phenomena may be connected.
}

@@

{\bf The transition exhibited by theoretical magnetic models can be explained by a rapid thinning of outer convective envelopes in stars with masses above about 1.2 $M_{\odot}$ \citep[e.g.,][]{Iben1965}. Once a star reaches an effective temperature of 6\,000 K, it has a very small or non-existent convective envelope, as shown in Fig.~\ref{fig:rad_core}(b). Figures~\ref{fig:rad_core}(a) and (b) show this is independent of age and mass, a fact arising as a result of the hydrogen ionization zone becoming increasingly localized near the optical photosphere with increasing effective temperature. In the absence of a convective envelope, magnetic inhibition of convection is irrelevant. Therefore, any differences observed between magnetic and standard stellar model isochrones at this effective temperature are the result of the magnetic field's influence on stellar structure at earlier evolutionary phases (i.e., delayed contraction). This provides a natural explanation for the convergence of the 10 Myr magnetic and standard model isochrones that occurs near this effective temperature in Fig.~\ref{fig:ages}(b). 
It then seems reasonable to posit that the shallow slope of the empirical HR diagram and the observed transition in the magnetic models trace the demise of outer convective envelopes and the growth of radiative cores in young, pre-main-sequence stars.}

{\bf While the demise of outer convection zones explains the final convergence of magnetic and standard models, it doesn't necessarily explain the beginning of the transition between  4\,500~K and 5\,000~K. Figures~\ref{fig:ages}(a) and \ref{fig:rad_core}(b) indicate that stars with \teff~<~4\,500~K can possess radiative cores that comprise up to about 75\% of the star, by mass.}

{\bf In the transition region, magnetic models have masses between 1.26 $M_{\odot}$ and 1.40 $M_{\odot}$. Magnetic models predict that these stars have radiative core masses between 76\% and 88\% of their total stellar mass, respectively (see Figure~\ref{fig:rad_core}a). The 1.40 $M_{\odot}$ model is of particular note, as Figure~\ref{fig:mrd} suggests that 1.40 $M_{\odot}$ stars are entering a brief period of radius inflation that accompanies the increasing energy generation from the $p$-$p$ chain and CN-cycle burning prior to the onset of core convection \citep[e.g.,][]{Iben1965,Bodenheimer1965}. Photospheric gas pressures rapidly drop during this phase of evolution bringing about a rapid drop in surface equipartition magnetic field strengths. As expected, a rapid decrease in equipartition magnetic field strengths is observed among the data in Table~\ref{tab:equip_values} beginning around 1.40 $M_{\odot}$. Stars above 1.40 $M_{\odot}$ become less sensitive to magnetic inhibition of convection because their magnetic fields are intrinsically weaker.}

%{\bf Disagreement between model predictions and the properties observed for F-type stars raises concerns about the validity of model predictions during this brief radius inflation phase. Possible reasons for these errors are discussed in Sect.~\ref{sec:radius}. If it }

{\bf If the transition region begins around 4\,500~K, as one might expect from the knee in the empirical HR diagram (Fig.~\ref{fig:empirical}), a rapid decrease in surface magnetic field strengths cannot fully explain the start of the transition. Note that Fig.~\ref{fig:rad_core}(c) suggests that the difference in size between radiative cores in magnetic and standard stellar models occurs around $T_{\rm eff} \sim 4\,500$~K, suggesting there is something relatively unique occurring at that effective temperature. However, Fig.~\ref{fig:ages} shows no noticeable change in morphology at  $T_{\rm eff} \sim 4\,500$~K. Another mechanism must be responsible for the failure of magnetic models to reproduce the sharp transition.} 
%suggests the mechanism is not accounted for in the models.}

{\bf The sharp knee at \teff~=~4\,500~K in Fig.~\ref{fig:empirical} may be the result of a global change in magnetic field topology. Evidence for this comes from \citet{Gregory2012}, who noted that large-scale magnetic field topologies observed on pre-main-sequence stars appear to correlate with their predicted radiative core mass. Specifically, they noted a shift from predominantly dipolar axisymmetric magnetic field topologies to multi-polar non-axisymmetric field topologies when the estimated radiative core mass $M_{\rm rad.\ core} > 0.4 M_\star$. It was noted above that at \teff~=~4\,500~K, magnetic models predict a star with $M_{\star} = 1.26 M_{\odot}$ and $M_{\rm rad.\ core} \approx 0.76 M_{\star}$, well above the predicted radiative core mass where stars are expected to shift toward multi-polar non-axisymmetric field topologies.}

{\bf However, \citet{Gregory2012} used non-magnetic models \citep{Siess2000} to establish a relationship between magnetic field topology and stellar interior structure. Hypothetically, if they were to observe a star in Upper Scorpius with \teff~=~4\,500~K, their HR diagram analysis would suggest that the star is approximately 5 Myr old. Figures~\ref{fig:rad_core}(a) and (b) reveal that a star with \teff~=~4\,500~K at 5 Myr is expected to have a mass of $M_{\star} = 1.10 M_{\odot}$ with $M_{\rm rad.\ core} \approx 0.43 M_{\star}$. This radiative core mass corresponds to 39\% of the total stellar mass and is consistent with the boundary identified by \citet{Gregory2012}.}

{\bf The implications of this results are that: (1) the knee observed in Fig.~\ref{fig:empirical} may be the result of a change in magnetic field topology and (2) the shift in magnetic field topology from a predominantly axisymmetric configuration to a non-axisymmetric configuration may occur when the radiative core mass is much larger than initially suggested. Magnetic models suggest the shift in global magnetic field topology occurs when $M_{\rm rad.\ core} / M_{\star} \approx 0.75$ as compared to $M_{\rm rad.\ core} / M_{\star} \approx 0.40$ \citep{Gregory2012}.}

%Third, pushing the transition in magnetic field topology to higher radiative core masses may provide an explanation for anomalous rotation periods observed among old main-sequence field stars \citep{vanSaders2016}.}
%{\bf If the large-scale magnetic field topology of pre-main-sequence stars shifts from predominantly axisymmetric to non-axisymmetric as the radiative core grows beyond 75\% of the total stellar mass, it is conceivable that the reverse is also true. That is, as convective envelopes grow along the sub-giant branch, large-scale magnetic fields may shift from predominantly multi-polar non-axisymmetric toward dipolar axisymmetric topologies. The shift in magnetic field topology may affect magnetic wind breaking mechanisms causing stars to exhibit anomalous rotation periods at older ages \citep{vanSaders2016}. This hypothesis may be at odds with the dependence of magnetic wind breaking mechanisms on large-scale magnetic field topologies, which suggest dipolar magnetic fields exert a greater torque on a star than multi-polar fields \citep[e.g.,][]{Reville2015}. However, it is unclear how the transition from a non-axisymmetric to axisymmetric magnetic field topologies affects this picture.}

{\bf This discussion is premised on the reality of the apparent transition at \teff~=~4\,500~K and the demise of convective envelopes producing the shallower slope in the empirical HR diagram. The shallower slope may be an artifact of how the empirical locus was computed. The empirical HR diagram is somewhat under-populated in the immediate vicinity of \teff~$= 5\,500$~K, raising the possibility that the running median has artificially created a smooth transition between warmer and cooler stars. However, the HR diagram is well-populated at slightly warmer and slightly cooler temperatures, suggesting the two regions must be somehow connected. While the precise morphology of the HR diagram in this region may be subject to alteration with additional data, the general trend should be robust against errors in how the empirical locus is computed.}

{\bf Errors transforming from photometric colors or spectral types to effective temperatures may provide a plausible explanation for the shallower slope of the HR diagram in the vicinity of 5\,000~K. Below this temperature, stellar atmospheric opacity becomes increasingly dominated by molecular species, particularly TiO in the optical and H$_2$O in the infrared, which poses problems when attempting to derive a robust effective temperature scale. This is particularly problematic for the HR diagram shown in Fig.~\ref{fig:empirical} because stars above \teff$ \sim 5\,000$~K were transformed from the observational to theoretical plane by different authors (\citealt{Pecaut2012} at warmer temperatures and \citealt{Preibisch1999} at cooler temperatures). If the effective temperature scale adopted by \citet{Preibisch1999} for cool stars is too cool by about 200 K, the observed transition might disappear and low-mass K- and M-type stars would fall closer to the 10 Myr standard model isochrone.

\citet{Preibisch1999} constructed an spectral type to effective temperature transformation at a gravity intermediate between dwarf and giant scales using the transformation derived for luminosity class IV objects by \citet{deJager1987}. This temperature scale is consistent with the more recent scale of \citet{Herczeg2015} who used PHOENIX BT-Settl model atmospheres \citep{Allard2011} to infer effective temperatures from photometric colors. Agreement between empirical methods and theoretical predictions is reassuring. However,
comparing these results to the 5 -- 30 Myr pre-main-sequence star temperature scale proposed by \citet{Pecaut2013}, one finds that the temperature scale adopted by \citeauthor{Preibisch1999} is about 100~K cooler for early K-type stars, but the two temperature scales agree around spectral type M0. For early-to-late M-type stars, \citeauthor{Preibisch1999} find temperatures about 100~K warmer than \citet{Pecaut2013}, a reversal from the comparison for late-K-type stars. Considering these differences, the sharp knee feature in the HR diagram may be accentuated by the adoption of an erroneous temperature scale, but it does not appear sufficient to fully explain the shallower slope observed in the HR diagram.
}

{\bf The observed knee and shallower slope in Fig.~\ref{fig:empirical} appear to be real features. General agreement between the behavior of the magnetic model isochrone and the observed stellar locus provides evidence that magnetic inhibition of convection is the mechanism that is producing these effects. This means that magnetic fields may be responsible for the age discrepancy between the high- and low-mass stellar populations in young associations. However, it is clear that this statement only holds with respect to the plausible identification of a general mechanism as the models fail to reproduce the precise morphology at the ``magnetic sequence turn-off.'' This is perhaps because magnetic models do not account for shifts in global magnetic field topology.}
If the age difference between warmer and cooler stars in Upper Scorpius is the result of magnetic inhibition of convection, the transition region between $4\,500 <$ \teff/K $< 6\,000$ provides an excellent laboratory for studying magnetic dynamo evolution as a function of {\bf stellar surface convection zone properties.}

%If this is the case, it may help explain the significant gap between the end of the magnetic stellar evolution isochrone and the location of HD 144548 A in the HR diagram. The mass difference is only $0.16\pm0.04$ \msun, but the temperature difference is nearly 1600~K. By contrast, the expected difference is 500~K from standard models. It's interesting to note that the end of the magnetic 10 Myr isochrone is where stars are expected to begin a brief period of radius inflation prior to ignition of the CN cycle (see below). This is shown in Fig.~\ref{fig:bump}. Radius inflation occurs over a 3 -- 4 Myr timespan and may result in a gradual decrease of the magnetic field strength throughout the stellar envelope due to a roughly 30\% decrease in the envelope's angular velocity. The latter is due to an increase in the envelope's moment of inertia and may weaken magnetic dynamo processes. One might then expect a gradual reduction in the importance of magnetic inhibition of convection, creating a situation where stars in a narrow mass range span a relatively large range in effective temperature, resulting in the gap seen in Fig.~\ref{fig:ages}a.

\subsection{Initial Mass Function}
The presence of magnetic and non-magnetic sequences has implications for the (sub)stellar initial mass function of Upper Scorpius \citep{Ardila2000, Preibisch2002}. {\bf Section~\ref{sec:results} described how magnetic inhibition of convection predominantly shifts stars of a given mass to cooler temperatures. As a result, stars with a given effective temperature and luminosity have a higher mass when magnetic inhibition of convection is considered. Furthermore, the presence of a transition region characterized by gradually declining influence of stellar magnetic fields that links the magnetic and non-magnetic sequences will tend spread stars with similar masses across a larger effective temperature domain.

>>>>

A 10 Myr magnetic isochrone naturally explains the factor of two age difference observed between high- and low-mass stars, provided the high-mass stars are not appreciably affected by additional non-standard physics (e.g., rotation). 
Figures~\ref{fig:ages}a and \ref{fig:ages}c (HR diagrams) show that a 10 Myr isochrone computed with equipartition magnetic fields is shifted toward cooler temperatures and higher luminosities compared to a 10 Myr non-magnetic isochrone. Inhibition of convection by magnetic fields cools the stellar surface temperature thereby slowing the contraction rate of young stars. Stars have a larger radius and a higher luminosity at a given age, as a result. The combination of cooler surface temperatures and higher luminosities makes a 10 Myr magnetic isochrone look nearly identical to a 5 Myr non-magnetic isochrone for stars with effective temperatures below about 5\,000~K. The magnetic stellar model isochrone lies on top of the 5 Myr standard model isochrone in Figs.~\ref{fig:ages}a and \ref{fig:ages}c and entirely within the empirical stellar locus for low-mass stars in Upper Scorpius.

The magnetic model isochrone also correctly converges toward the 10 Myr standard model isochrone at warmer effective temperatures. To some degree, this  convergence reproduces an observed transition in the empirical HR diagram where the age inferred from standard model isochrones shifts from 5 Myr to 10 Myr. Below \teff~$\sim 5\,000$~K, the magnetic isochrone closely matches predictions from a 5 Myr standard model isochrone. Compare this to the small segment of the magnetic isochrone above \teff\ $\sim 6\,000$~K. Here, the magnetic isochrone traces the 10 Myr standard model isochrone. Although the model predicted transition appears to occur over approximately the correct effective temperature domain, Fig.~\ref{fig:ages}a shows a sharper transition from a magnetic to a non-magnetic sequence between $4\,500 <$ \teff/K $< 6\,000$ compared to model predictions. This is more clearly seen in Fig.~\ref{fig:empirical}, where the empirical median stellar locus exhibits a knee around \teff $\sim 4\,500$~K that roughly corresponds to the beginning of the transition region in Fig.~\ref{fig:ages}a. A distinct knee feature is absent from the magnetic model isochrone.

\begin{figure}[t]
    \centering
    \includegraphics[width=0.90\linewidth]{USCO5_MR.eps}
    \caption{Mass-radius diagram for stars in eclipsing systems. Black points are from \citet{Kraus2015} and \citet{Alonso2015}, while gray points are taken from \citet{Lodieu2015} and \citet{David2016}. Model predictions for magnetic and non-magnetic isochrones are the same as in Fig.~\ref{fig:ages}.}
    \label{fig:mrd}
\end{figure}

Moreover, inspection of the mass-radius diagram in Figure~\ref{fig:mrd} shows a 10 Myr magnetic isochrone provides reasonable agreement with the two low-mass eclipsing binary systems. It is apparent that magnetic inhibition of convection leads to more significant radius ``inflation'' at higher masses compared to at lower masses. This effect leads to a change in slope of the model predicted mass-radius relationship that is consistent with observations. Although agreement is good, it is not perfect. Depending on whether mass and radius estimates are adopted from \citet{Kraus2015} or \citet{David2016}, at 10 Myr the radii of the primary and secondary in UScoCTIO5 are either 3.2\% and 2.1\% (\citeauthor{Kraus2015}) larger than model predictions or 5.7\% and 6.6\% larger (\citeauthor{David2016}). Similarly, models at 10 Myr predict radii that are 1.4\% too large and 1.5\% too small for the Ba and Bb components of HD 144548 at 10 Myr, respectively. An age between 9.0 and 9.5 Myr is preferred for UScoCTIO5, while 10 Myr is the best fit age for HD 144548 Ba/Bb.

This age spread could be indicative of an intrinsic age spread, but it is also possible to attribute this spread to errors in the mass and radius determinations of the eclipsing binary systems or to the fact that the low-mass stars in UScoCTIO5 may require marginally stronger magnetic field strengths than are predicted from equipartition arguments. Nevertheless, it is encouraging that models provide this level of agreement with an age and surface magnetic field strengths determined \emph{a priori}.

\section{Discussion}
\label{sec:disc}
An age of 9 -- 10 Myr gives broad agreement across the HR and mass-radius diagrams. No stellar population in Upper Scorpius studied here robustly supports the possibility that the median age of the association is 5 Myr. There are, however, still age discrepancies that must be addressed. As noted above, the median age {\bf inferred from} F-type stars appears to be a few million years older than {\bf the median age inferred from} stars of other spectral types. This discrepancy is perplexing and deserves further investigation, especially considering that {\bf physics potentially missing from the models} would likely conspire to {\bf increase the age inferred from} F-stars. It should be noted that most F-type stars in Upper Scorpius are at a stage of evolution where models predict radii increase and subsequently decrease over a period of roughly 4 -- 8 Myr. The timescale for this process is similar to the observed age discrepancy (see Fig.~\ref{fig:bump} in Sect.~\ref{sec:radius}) and may be indicative of potential shortcomings in existing model physics such as radiative opacities or nuclear reaction cross-sections.

Age discrepancies also exist with two B-type members of Upper Scorpius: \object{$\tau$ Sco} and \object{$\omega$ Sco}. They exhibit ages between 2 and 5 Myr depending on whether rotation is accounted for in stellar evolution models \citep{Pecaut2012}. Those authors show that there are four other B-type stars that have inferred ages consistent with the 10 Myr median age proposed here, if rotation is taken into account. Notably the four stars that appear older are known binary systems while the two seemingly younger stars do not have a detected companion \citep{Pecaut2012}. The presence of two seemingly young B-type stars may be leveraged to suggest there exists a young population of stars with ages around 5 Myr thus supporting the younger age for the low-mass stellar population and thereby doing away with the need for a magnetic field explanation. However, that scenario requires that the low-mass stars form almost exclusively in a later star formation episode than the higher mass population. Although we cannot definitively rule out this scenario, we find it unlikely and maintain that the median age for the low-mass stars is too young compared to the rest of the stellar population in the absence of magnetic inhibition of convection.

\subsection{Magnetic Field Evolution \& Radiative Core Growth}
\label{sec:dynamo}
Figure~\ref{fig:ages} shows that a 10 Myr magnetic model isochrone agrees with predictions from a 5 Myr standard model isochrone for effective temperatures below about 5\,000~K, but traces a 10 Myr standard model isochrone above 6\,000~K. This suggests that magnetic inhibition of convection plays an important role in dictating the structure of cool low-mass stars, but the structure of warmer high-mass stars is relatively insensitive to the influence of magnetic fields. In between these two regimes, models predict a transition in which stars appear to exhibit a decreasing sensitivity to magnetic inhibition of convection as effective temperature increases.

As was noted in Sect.~\ref{sec:results}, Figs.~\ref{fig:empirical} and \ref{fig:ages}a indicate that a similar transition occurs over roughly the same effective temperature domain in the empirical HR diagram of Upper Scorpius. Early- to mid-G stars in Upper Scorpius (\teff$ \sim 6\,000$~K) are best described by a 10 Myr standard stellar model isochrone. Instead of continuing to follow a 10 Myr standard model isochrone, late-G stars appear to be better represented by an isochrone intermediate between 5 and 10 Myr. This causes the empirical sequence to exhibit a shallower slope than standard model predictions between $5\,750 > T_{\rm eff} / {\rm K} > 4\,500$. That the shallower slope in the empirical HR diagram and the transition predicted by magnetic stellar models are coincident, suggests that the two phenomena may be connected.

@@

The transition exhibited by theoretical magnetic models can be explained by a rapid thinning of outer convective envelopes in stars with masses above about 1.2 $M_{\odot}$ \citep[e.g.,][]{Iben1965}. Once a star reaches an effective temperature of 6\,000 K, it has a very small or non-existent convective envelope, as shown in Fig.~\ref{fig:rad_core}(b). Figures~\ref{fig:rad_core}(a) and (b) show this is independent of age and mass, a fact arising as a result of the hydrogen ionization zone becoming increasingly localized near the optical photosphere with increasing effective temperature. In the absence of a convective envelope, magnetic inhibition of convection is irrelevant. Therefore, any differences observed between magnetic and standard stellar model isochrones at this effective temperature are the result of the magnetic field's influence on stellar structure at earlier evolutionary phases (i.e., delayed contraction). This provides a natural explanation for the convergence of the 10 Myr magnetic and standard model isochrones that occurs near this effective temperature in Fig.~\ref{fig:ages}(b). It then seems reasonable to posit that the shallow slope of the empirical HR diagram and the observed transition in the magnetic models trace the demise of outer convective envelopes and the growth of radiative cores in young, pre-main-sequence stars.

While the demise of outer convection zones explains the final convergence of magnetic and standard models, it doesn't necessarily explain the beginning of the transition that occurs between $T_{\rm eff} = $4\,500~K and 5\,000~K.  
In the transition region, magnetic models have masses between 1.26 $M_{\odot}$ ($T_{\rm eff} = $ 4\,500~K) and 1.40 $M_{\odot}$ ($T_{\rm eff} = $5\,000~K). Magnetic models predict that these stars have radiative core masses between 76\% and 88\% of their total stellar mass, respectively (see Figure~\ref{fig:rad_core}a). The 1.40 $M_{\odot}$ model is of particular note, as Figure~\ref{fig:mrd} suggests that 1.40 $M_{\odot}$ stars are entering a brief period of radius inflation that accompanies the increasing energy generation from the $p$-$p$ chain and CN-cycle burning prior to the onset of core convection \citep[e.g.,][]{Iben1965,Bodenheimer1965}. Photospheric gas pressures rapidly drop during this phase of evolution bringing about a rapid drop in surface equipartition magnetic field strengths. As expected, a rapid decrease in equipartition magnetic field strengths is observed among the data in Table~\ref{tab:equip_values} beginning around 1.40 $M_{\odot}$. Stars above 1.40 $M_{\odot}$ become less sensitive to magnetic inhibition of convection because their magnetic fields are intrinsically weaker.

If the transition region begins around 4\,500~K, as one might expect from the knee in the empirical HR diagram (Fig.~\ref{fig:empirical}), a rapid decrease in surface magnetic field strengths cannot fully explain the start of the transition. Note that Fig.~\ref{fig:rad_core}(c) suggests that the difference in size between radiative cores in magnetic and standard stellar models occurs around $T_{\rm eff} \sim 4\,500$~K, suggesting there is something relatively unique occurring at that effective temperature. However, Fig.~\ref{fig:ages} shows no noticeable change in morphology at  $T_{\rm eff} \sim 4\,500$~K. Another mechanism must be responsible for the failure of magnetic models to reproduce the sharp transition.

The sharp knee at \teff~=~4\,500~K in Fig.~\ref{fig:empirical} may be the result of a global change in magnetic field topology. Evidence for this comes from \citet{Gregory2012}, who noted that large-scale magnetic field topologies observed on pre-main-sequence stars appear to correlate with their predicted radiative core mass. Specifically, they noted a shift from predominantly dipolar axisymmetric magnetic field topologies to multi-polar non-axisymmetric field topologies when the estimated radiative core mass $M_{\rm rad.\ core} > 0.4 M_\star$. It was noted above that at \teff~=~4\,500~K, magnetic models predict a star with $M_{\star} = 1.26 M_{\odot}$ and $M_{\rm rad.\ core} \approx 0.76 M_{\star}$, well above the predicted radiative core mass where stars are expected to shift toward multi-polar non-axisymmetric field topologies.

However, \citet{Gregory2012} used non-magnetic models \citep{Siess2000} to establish a relationship between magnetic field topology and stellar interior structure. Hypothetically, if they were to observe a star in Upper Scorpius with \teff~=~4\,500~K, their HR diagram analysis would suggest that the star is approximately 5 Myr old. Figures~\ref{fig:rad_core}(a) and (b) reveal that a star with \teff~=~4\,500~K at 5 Myr is expected to have a mass of $M_{\star} = 1.10 M_{\odot}$ with $M_{\rm rad.\ core} \approx 0.43 M_{\star}$. This radiative core mass corresponds to 39\% of the total stellar mass and is consistent with the boundary identified by \citet{Gregory2012}.

The implications of this results are that: (1) the knee observed in Fig.~\ref{fig:empirical} may be the result of a change in magnetic field topology and (2) the shift in magnetic field topology from a predominantly axisymmetric configuration to a non-axisymmetric configuration may occur when the radiative core mass is much larger than initially suggested. Magnetic models suggest the shift in global magnetic field topology occurs when $M_{\rm rad.\ core} / M_{\star} \approx 0.75$ as compared to $M_{\rm rad.\ core} / M_{\star} \approx 0.40$ \citep{Gregory2012}.

This discussion is premised on the reality of the apparent transition at \teff~=~4\,500~K and the demise of convective envelopes producing the shallower slope in the empirical HR diagram. The shallower slope may be an artifact of how the empirical locus was computed. The empirical HR diagram is somewhat under-populated in the immediate vicinity of \teff~$= 5\,500$~K, raising the possibility that the running median has artificially created a smooth transition between warmer and cooler stars. However, the HR diagram is well-populated at slightly warmer and slightly cooler temperatures, suggesting the two regions must be somehow connected. While the precise morphology of the HR diagram in this region may be subject to alteration with additional data, the general trend should be robust against errors in how the empirical locus is computed.

Errors transforming from photometric colors or spectral types to effective temperatures may provide a plausible explanation for the shallower slope of the HR diagram in the vicinity of 5\,000~K. Below this temperature, stellar atmospheric opacity becomes increasingly dominated by molecular species, particularly TiO in the optical and H$_2$O in the infrared, which poses problems when attempting to derive a robust effective temperature scale. This is particularly problematic for the HR diagram shown in Fig.~\ref{fig:empirical} because stars above \teff$ \sim 5\,000$~K were transformed from the observational to theoretical plane by different authors (\citealt{Pecaut2012} at warmer temperatures and \citealt{Preibisch1999} at cooler temperatures). If the effective temperature scale adopted by \citet{Preibisch1999} for cool stars is too cool by about 200 K, the observed transition might disappear and low-mass K- and M-type stars would fall closer to the 10 Myr standard model isochrone.

\citet{Preibisch1999} constructed an spectral type to effective temperature transformation at a gravity intermediate between dwarf and giant scales using the transformation derived for luminosity class IV objects by \citet{deJager1987}. This temperature scale is consistent with the more recent scale of \citet{Herczeg2015} who used PHOENIX BT-Settl model atmospheres \citep{Allard2011} to infer effective temperatures from photometric colors. Agreement between empirical methods and theoretical predictions is reassuring. However, comparing these results to the 5 -- 30 Myr pre-main-sequence star temperature scale proposed by \citet{Pecaut2013}, one finds that the temperature scale adopted by \citeauthor{Preibisch1999} is about 100~K cooler for early K-type stars, but the two temperature scales agree around spectral type M0. For early-to-late M-type stars, \citeauthor{Preibisch1999} find temperatures about 100~K warmer than \citet{Pecaut2013}, a reversal from the comparison for late-K-type stars. Considering these differences, the sharp knee feature in the HR diagram may be accentuated by the adoption of an erroneous temperature scale, but it does not appear sufficient to fully explain the shallower slope observed in the HR diagram.

The observed knee and shallower slope in Fig.~\ref{fig:empirical} appear to be real features. General agreement between the behavior of the magnetic model isochrone and the observed stellar locus provides evidence that magnetic inhibition of convection is the mechanism that is producing these effects. This means that magnetic fields may be responsible for the age discrepancy between the high- and low-mass stellar populations in young associations. However, it is clear that this statement only holds with respect to the plausible identification of a general mechanism as the models fail to reproduce the precise morphology at the ``magnetic sequence turn-off.'' This is perhaps because magnetic models do not account for shifts in global magnetic field topology. If the age difference between warmer and cooler stars in Upper Scorpius is the result of magnetic inhibition of convection, the transition region between $4\,500 <$ \teff/K $< 6\,000$ provides an excellent laboratory for studying magnetic dynamo evolution as a function of stellar surface convection zone properties.

\subsection{Initial Mass Function}
The presence of magnetic and non-magnetic sequences has implications for the (sub)stellar initial mass function of Upper Scorpius \citep{Ardila2000, Preibisch2002}. Section~\ref{sec:results} described how magnetic inhibition of convection predominantly shifts stars of a given mass to cooler temperatures. As a result, stars with a given effective temperature and luminosity have a higher mass when magnetic inhibition of convection is considered. Furthermore, the presence of a transition region characterized by gradually declining influence of stellar magnetic fields that links the magnetic and non-magnetic sequences will tend spread stars with similar masses across a larger effective temperature domain.
